Realizing temporal graphs from fastest travel times

### 2024-01-19 Figures/fig-fpt-equivClass.tex
added fig for proof of the equivalence classes

	\begin{tikzpicture}
		%%%S_uv
		\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
		\node[vert,label=above:$v_2$] (v2) at (2,0) {};
		\node[vert,label=above:$v_i$] (vi) at (3,0) {};
		\node[vert,label=above:$v_{i+1}$] (vi+1) at (3.8,0) {};
		\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
		\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
		\draw (v1) -- (v2) -- (vi) -- (vi+1) -- (vp1) -- (vp);

		%%%% node w
		\node[vert,label=below:$w$] (w) at (4,-3) {};

		\draw [blue] 
		(w) edge[dirwave] [out=160,in=285] (v1) 
		(v1) -- (v2)
		(v2) edge[diredge2] (vi);

		\draw [red]
		(w) edge[dirwave] [out=20,in=255] (vp) 
		(vp) -- (vp1)
		(vp1) edge[diredge2] (vi+1);

>>>>

	\begin{tikzpicture}

		\node [vert,label=below:$x$] (x) at (0, 0) {};
		\node [vert,label=below:$z_2$] (z2) at (-1.5, 1) {};
		\node [vert,label=above:$z_1$] (z1) at (-1.5, -1) {};
		\node [vert,label=below:$y$] (y) at (7, 0) {};

		\draw (z1) edge[] node[below, yshift=-1mm, text=black] {$t_1$}  (x);
		\draw (z2) edge[] node[above, yshift= 1mm,  text=black] {$t_2$} (x);
		\draw [red]
		(x) edge[] [bend right] node[below, text=black] {$P$} 
		node[vert, pos=0.87, color=black, fill=white] {}
		node[pos=0.96,below, text=black] {$t_p$} (y) ;
		\draw [blue]
		(x) edge[] [bend left] node[above, text=black] {$Q$} 
		node[vert, pos=0.87, color=black, fill=white] {}
		node[pos=0.96,above, text=black] {$t_q$}
		(y) ;
